\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 package.
%% See http://texdoc.net/pkg/fontawesome5 for full list of symbols.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

\usepackage{paracol}
\usepackage{microtype}

\hyphenation{Mersateb}

\pretolerance=100
\tolerance=10000

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Lato}
\else
  % If using pdflatex:
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{DarkBlue}{HTML}{00008b}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{3B3B3B}
% \colorlet{name}{black}
% \colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkBlue}
\colorlet{headingrule}{DarkBlue}
% \colorlet{subheading}{PastelRed}
\colorlet{accent}{DarkBlue}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\begin{document}
\name{Mohammad Saadatfar}
\tagline{Senior Electronics Engineer}
%\photoR{2.5cm}{profile}
\personalinfo{%
  \email{mh.saadatfar@gmail.com}
  \homepage{https://mhsaadatfar.dev}
  \linkedin{https://linkedin.com/in/mhsaadatfar}
  %\birthday{1993 (29 years old)}
  \location{Burnaby, Canada}
  \phone{+1-236-838-0318}
  %\phone{+90-5067521731}
}

\makecvheader

%% Depending on your tastes, you may want to make fonts of e environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

\columnratio{0.5}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.

\cvsection{About Me}
\vbox{ %
\justifying \noindent With over 12 years in electronic system design, I served as the Ex-CTO of Mersateb Co., a small-sized medical device manufacturer. Directed and mentored a team of 10+ engineers, involving hands-on participation in coding and design. Successfully launched 6 products, establishing our company as a top producer of dermatology devices. Led 5+ quality assurance team members and achieved certifications such as IEC 62304 and Medical CE Certification.
}
\medskip


%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}


\vbox{ %
	\cvevent
	{Mersateb Co. \link{https://mersateb.com/en}{\faExternalLink*}}
	{CTO, Co Founder}
	{2015 -- Ongoing}{Tehran, Iran \& Istanbul, Turkiye}
	\begin{itemize}
		\item Led and mentored a team of 10+ R\&D and engineering professionals, actively contributing to coding and design, and successfully launched 6 medical device products such as Electrosurgical Plasma, Fractional Micro Needling Radio Frequency, Vaginal Radio Frequency, Carboxy Therapy, and Termo Fractional Device \link{https://mhsaadatfar.dev/download/Catalog/Mersateb.pdf}{(Download Catalogs\faExternalLink*)}.
		\item Designed and developed 6+ software systems including GUIs for the Android and Windows platforms.
		\item Coded 10+ embedded software firmware in C for devices, quality control, and test boards, using ARM, AVR, and FreeRTOS platforms.
		\item Standardized 4 software systems based on IEC 62304 (Medical device software — Software life cycle processes).
		\item Led 5 quality assurance team members as Management Representative and certified ISO 13485, ISO 9001, Low Voltage Device Certification (LVD 2014/35/EU), and Medical CE Certification (MDD 93/42/EEC).
		\item Hired 100+ employees (40+ active). Became the leading producer of dermatology devices in Iran with 1000+ active installations worldwide and exported to European countries including Turkey and Spain.
	\end{itemize}	
	\divider
}

\vbox{ %
	\cvevent
	{Faradars Online Courses \link{https://faradars.org/courses/fvee9406-pcb-design-using-altium-designer}{\faExternalLink*}}
	{Teacher}
	{2015}{}
	\begin{itemize}
		\item Instructed 9000+ students in 'Printed Circuit Board Assembly (PCBA) Design using Altium Designer.' The course received a 4.3/5 rating based on student reviews.
		\link{https://faradars.org/courses/fvee9406-pcb-design-using-altium-designer}{\faExternalLink*}
		\item Instructed 1300+ students in 'Electrical Circuit Simulation using OrCad,' earning an average rating of 4.8 out of 5 based on student reviews.
		\link{https://faradars.org/courses/fvee9409-electrical-circuits-simulation-using-orcadr}{\faExternalLink*}
	\end{itemize}
	\divider
}

\vbox{ %
	\cvevent{Freelancer}
	{Electronics System Engineer and Embedded Developer}
	{2011-2015}{}
	\begin{itemize}
		\item completed 5+ projects, including the development of 3 industrial QC and monitoring systems, a kart lab timing system, and a remotely-operated underwater vehicle.
		\item Utilized technologies and tools such as Programmable Logic Controllers (PLC), Field Programmable Gate Arrays (FPGA), AVR, and ARM microcontrollers, as well as the LabVIEW development environment.
	\end{itemize}
	\divider
}

\vbox{ %
	\cvevent{Power Electronics - University of Tehran \link{https://ut.ac.ir/en}{\faExternalLink*}}
	{Chief Teacher Assistant}
	{2015}{}
	\begin{itemize}
		\item Lectured in 15+ laboratory sessions (1 per week) and authored course lab materials.
		\item Directed exam grading team (Final, Midterm, and 4+ quizzes).
	\end{itemize}
	\divider
}

\vbox{ %
	\cvevent
	{University of Tehran \link{https://ut.ac.ir/en}{\faExternalLink*}}
	{Teacher Assistant}
	{2014}{}
	Courses:
	\smallskip
	\begin{itemize}
		\item Electronics 1
		\item Microprocessors
	\end{itemize}
	\divider
}

%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vbox{ %
	\cvsection{Projects}
	\cvproject{Solatrix™ Fractional Thermo-mechanical Device}{https://mhsaadatfar.dev/download/Catalog/Solatrix.pdf}{2021}
	\justifying \noindent
	Solatrix is a fractional thermo-mechanical device that rejuvenates and removes skin lesions by transferring heat to the skin through a high-temperature titanium tip, stimulating collagen production.
	\medskip
	\begin{itemize}
		\item Designed $\sim$1x1cm high-temperature (+400°C) titanium tip warmer and cooling system.
		\item Developed using fast ($\sim$3m/s) DC linear servomotor to improve safety and accuracy, Android embedded HMI, and ARM Cortex-M Processor.
	\end{itemize}	
}
\divider

\vbox{ %
	\cvproject{MadamX™ Vaginal RF Device}{https://mhsaadatfar.dev/download/Catalog/MadameX.pdf}{2020}
	\justifying \noindent
	MadamX uses safe electrodes to emit RF that increase the temperature of the underlying layers and muscles in the vagina, while EMS stimulates the natural neuro-muscular mechanisms in the pelvic floor.
	\medskip
	\begin{itemize}
		\item Pioneered featuring simultaneous 4MHz radio frequency and electrical muscle stimulation treatment.
	\end{itemize}
}
\divider

\vbox{ %
	\cvproject{Firebolt™ Plasma Device}{https://mhsaadatfar.dev/download/Catalog/Firebolt.pdf}{2018}
	\justifying \noindent
	The Firebolt plasma device is a high-safety device used for treatments such as Blepharoplasty, skin lesions removal, freckles, and wrinkles using high voltage/frequency plasma.
	\medskip
	\begin{itemize}
		\item Achieved top selling status for plasma device in Iran with 800+ active installations.
		\item Attained the highest frequency of 250KHz among similar devices using high-frequency, high-voltage ($\sim$5kV) power generator.
	\end{itemize}
}
\divider

\vbox{ %
	\cvproject{Nettle™ Fractional RF Device}{https://mhsaadatfar.dev/download/Catalog/Nettle.pdf}{2018}
	\justifying \noindent
	Fractional RF technology uses fractional needles to apply the high frequency voltage to stimulate collagen and elastin production in specific skin layers, leading to skin rejuvenation.
	\medskip
	\begin{itemize}
		\item Obtained license for the 1st and only fractional RF device manufactured in Iran and achieved 250+ active installations.
		\item Realized safe (FMEA) 4MHz, E-class variable load power radio frequency generator.
	\end{itemize}
}
\divider

\vbox{ %
	\cvproject{Hurricane™ Carboxytherapy Device}{https://mersateb.com/en/hurricane/}{2017}
	\justifying \noindent
	Hurricane initiates reactions through controlled CO2 injections resulting in vasodilation, increased blood flow and body temperature, oxygenation of the targeted area, increased metabolism and tissue rejuvenation, and decreased cellulitis.
	\medskip
	 \begin{itemize}
	 \item Validated <15mL injection volume accuracy.
	\end{itemize}
	 
}
\divider

\vbox{ %
	\cvproject{Remotely Operated Underwater Vehicle}{}{2014}
	\justifying \noindent
	\begin{itemize}
		\item Implemented using Xilinx FPGA, LabVIEW control and monitor panel, and DC Motor.
		\item Obtained 3rd place in IranOpen RoboCup ROV league 2014.
	\end{itemize}
	
}
\divider

\vbox{ %
	\cvproject{Latex Condom Inflation Burst Volume and Pressure Testing Equipment}{}{2015}
	\justifying \noindent
	\begin{itemize}
		\item Implemented precision pressure-volume graph monitor and automatic quality control report generator using LabVIEW software for monitoring panel, Mass flow sensor, and air pressure sensor.
	\end{itemize}
	
}
\divider

\vbox{ %
	\cvproject{Latex Condom Water Leak Testing Equipment Logger and Monitor System}{}{2015}
	\justifying \noindent
	\begin{itemize}
		\item Standardized according to ISO 4074:2002 using Delta PLC.
	\end{itemize}
	
}
\divider

\vbox{ %
	\cvproject{Production Line Product Counter}{}{2014}
	\justifying \noindent
	\begin{itemize}
		\item Developed using Siemens PLC LOGO! and infrared transceiver with ability to save history and Web panel monitor.
	\end{itemize}
	
}
\divider

\vbox{ %
	\cvproject{Kart Lap Timing System}{}{2011}
	\justifying \noindent
	\begin{itemize}
		\item Proposed 2 architecture using Magnetic and Inferred sensors with accuracy of <1mSec and performed using infrared transceiver and AVR microprocessor.
	\end{itemize}
	
}
\divider

%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vbox{ %
	\cvsection{Education}
	\cvevent{MSc in Power Electronics \& Electrical Machines}{University of Tehran}{2015 -- 2018}{}
	Thesis: Performance Improvement of Reactive Power Sharing in Photovoltaic Islanded Microgrids
	
	\divider
	
	\cvevent{BSc in Electrical Engineering}{University of Tehran}{2011 -- 2015}{}
	Major: Control \par
	Thesis: Optimizing the Motion of Soft Quadruped Robot Using Genetic Algorithm
	
	\divider
}

%%%%%%%%%% SKILLS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vbox{ %
	
	\cvsection{SKILLS}
	
		\cvskill{Embedded Engineering}{
		ARM, Keil,
		FreeRTOS,
		FPGA,
		Linux Kernel Programming, Buildroot
	}
	
	\cvskill{Electronics and Power Electronics}{
		Printer Circuit Board (PCB, PCBA)
		Altium Designer,
		OrCAD,
		LabVIEW,
		PowerSIM,
		MATLAB, Simulink,
		DC/DC and AC/DC Convertors,
		PLC
	}
	
	\cvskill{Programming Languages}{
		C, C++,
		Verilog,
		C\#,
		SQL,
		Javascript
	}
	
	
	\cvskill{Network}{
		CCNA,
		MTCNA
	}
	
	\cvskill{Regulation and Standards}{
		Medical Device CE (93/42/EEC),
		Low Voltage CE (2014/35/EU),
		ISO 13485, ISO 9001,
		ISO 14971 (Risk Management),
		IEC Standards,
		EMC
	}
	
	\cvskill{Project Management \& Analysis}{
		Agile (Scrum),
		Kanban,
		FMEA
	}
	
	\cvskill{Other Skills}{
		Fullstrack Web Development (ASP.Net, Vue.Js, Astro),
		Solidworks,
		Git,
		Docker,
		\LaTeX
	}
	
	\cvskill{Languages}{
		English, Persian
	}
}


%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\nocite{*}

\end{document}
